Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-17 paper.tex
Update paper.tex

\gmj{Might need to change the sunflower entry in this table.  The best evidence I can now point to for adaptive introgression is the reintroduction of the branching trait, but that example is not natural.}

@@

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
\gmj{Determination of adaptiveness could be accomplished genomically (looking for high LD regions that indicate selective sweeps, or by functional identification.}
%\gmj{Kinds of functional identification?  Knockout experiments, sequence homology with annotated genes, proximity to QTLs?}
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}

@@

Does one see different architectures of introgression across different regions?
Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation across these ranges?

>>>>

@@

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
\gmj{Determination of adaptiveness could be accomplished genomically (looking for high LD regions that indicate selective sweeps) or by functional identification.}
%\gmj{Kinds of functional identification?  Knockout experiments, sequence homology with annotated genes, proximity to QTLs?}
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}

@@

Does one see different architectures of introgression across different regions?
Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?
\gmj{Barley and maize most strongly show geographic patterns that we can talk about here, but I'm not sure how to discuss them again.}
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation across these ranges?
\gmj{Refer to the map and bar graph here?}
